---
title: "autothresholdr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
```

An R package for thresholding images. 

[![Travis-CI Build Status](https://travis-ci.org/rorynolan/autothresholdr.svg?branch=master)](https://travis-ci.org/rorynolan/autothresholdr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rorynolan/autothresholdr?branch=master&svg=true)](https://ci.appveyor.com/project/rorynolan/autothresholdr)
[![codecov](https://codecov.io/gh/rorynolan/autothresholdr/branch/master/graph/badge.svg)](https://codecov.io/gh/rorynolan/autothresholdr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/autothresholdr)](https://cran.r-project.org/package=autothresholdr)
![RStudio CRAN total downloads](http://cranlogs.r-pkg.org/badges/grand-total/autothresholdr)
[![RStudio CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/autothresholdr)](http://cran.rstudio.com/web/packages/autothresholdr/index.html)
[![Rdocumentation](http://www.rdocumentation.org/badges/version/autothresholdr)](http://www.rdocumentation.org/packages/autothresholdr)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

## Installation

### Linux

1. On **Ubuntu** (similarly for other debian **linux**), you need to do:
```
sudo apt-get update
sudo apt-get install libssl-dev libtiff5-dev libfftw3-dev 
sudo apt-get install libcurl4-openssl-dev libxml2-dev 
```

1. In R, run
```{r Install autothresholdr for Linux, eval=FALSE}
install.packages("autothresholdr")
```

### Windows

1. Go to https://cran.r-project.org/bin/windows/Rtools/ and install the latest version of Rtools.

1. In R, run
```{r Install autothresholdr for Windows, eval=FALSE}
install.packages("autothresholdr")
```

### Mac

In R, run
```{r Install autothresholdr for Mac, eval=FALSE}
install.packages("autothresholdr")
```

## Installing the development version
The release version is recommended (and installed with `install.packages("autothresholdr")` as above), but to install the development version, in R enter
```{r Install autothresholdr dev, eval=FALSE}
devtools::install_github("rorynolan/autothresholdr")
```

# Thresholding Images
Let's load `autothresholdr` and some friends.
```{r load libraries, results='hide'}
library(autothresholdr)
library(magrittr)
library(ijtiff)
```
We'll be using the image that comes with the package:
```{r the image}
img_matrix <- system.file("extdata", "fiji_eg.tif", 
                          package = "autothresholdr") %>%
  read_tif() %>% 
  {.[, , 1, 1]}
display(img_matrix)
```

It's a bit of a cell, the black part is where the cell is not. The threshold is supposed to tell us what is *dark* (not cell) and what is *bright* (cell). By playing around, we see that something like 20 might (for some purposes) be a good value.

```{r guess twenty}
display(img_matrix >= 20)
```

But what if we have many images and we don't want to *play around*, we want a method of calculating the threshold automatically. http://imagej.net/Auto_Threshold gives many such methods and they are provided to you in R via this package. Go to that webpage for a nice comparison of the methods.

The function `auto_thresh` finds the threshold, `auto_thresh_mask` gets the mask (an array with a `TRUE` for elements exceeding the threshold and `FALSE` elsewhere) and `auto_thresh_apply_mask` applies the mask to the original image by setting the elements that don't exceed the threshold to `NA`.

Let's see each with Huang thresholding.
i
```{r thresh mask apply}
auto_thresh(img_matrix, "h")
auto_thresh_mask(img_matrix, "h") %>% display()
auto_thresh_apply_mask(img_matrix, "h") %>% display()
```

In this last image, the `NA` pixels are white.

