---
title: "autothresholdr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
```

An R package for thresholding images. 

[![Travis-CI Build Status](https://travis-ci.org/rorynolan/autothresholdr.svg?branch=master)](https://travis-ci.org/rorynolan/autothresholdr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rorynolan/autothresholdr?branch=master&svg=true)](https://ci.appveyor.com/project/rorynolan/autothresholdr)
[![codecov](https://codecov.io/gh/rorynolan/autothresholdr/branch/master/graph/badge.svg)](https://codecov.io/gh/rorynolan/autothresholdr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/autothresholdr)](https://cran.r-project.org/package=autothresholdr)
![RStudio CRAN total downloads](http://cranlogs.r-pkg.org/badges/grand-total/autothresholdr)
[![RStudio CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/autothresholdr)](http://cran.rstudio.com/web/packages/autothresholdr/index.html)
[![Rdocumentation](http://www.rdocumentation.org/badges/version/autothresholdr)](http://www.rdocumentation.org/packages/autothresholdr)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![DOI](https://zenodo.org/badge/72632397.svg)](https://zenodo.org/badge/latestdoi/72632397)


## Installation

### `libtiff`

`autothresholdr` requires you to have the `libtiff` C library installed. To install `libtiff`:

* On __Debian Linux__, try `sudo apt-get install libtiff5-dev`, or if that fails, try  
`sudo apt-get install libtiff4-dev`.
* On __Fedora Linux__, try `sudo yum install libtiff5-dev`, or if that doesn't work, try  
`sudo yum install libtiff4-dev`.
* On __Mac__, you need [Homebrew](https://brew.sh/). Then in the terminal, run `brew install libtiff`.
* On __Windows__, go to https://cran.r-project.org/bin/windows/Rtools/ and install the latest version of Rtools. If you have 32-bit windows, you also need to install `libtiff` from http://gnuwin32.sourceforge.net/packages/tiff.htm.

### Installing the release version

You can install `autothresholdr` from CRAN (recommended) with:
```{r CRAN installation, eval=FALSE}
install.packages("autothresholdr")
```

### Installing the development version

You can install the development version from GitHub with:
```{r GitHub installation, eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("rorynolan/autothresholdr")
```

## Vignette
To learn how to use the package, consult the [vignette](https://cran.r-project.org/web/packages/autothresholdr/vignettes/autothresholdr.html). 

## Contribution
Contributions to this package are welcome. The preferred method of contribution is through a github pull request. Feel free to contact me by creating an issue. Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
