---
title: "autothresholdr"
author: "Rory Nolan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autothresholdr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7, fig.height = 6
)
```

# Thresholding Images
This is a package for thresholding images. Let's load it and some friends.
```{r load libraries, results='hide'}
library(autothresholdr)
library(ijtiff)
library(magrittr)
```
We'll be using the image that comes with the package:
```{r the image}
img <- read_tif(system.file("extdata", "fiji_eg.tif", 
                            package = "autothresholdr"))
dim(img)
display(img[, , 1, 1])  # first channel, first frame
```

It's a bit of a cell, the black part is where the cell is not. The threshold is supposed to tell us what is *dark* (not cell) and what is *bright* (cell). By playing around, we see that something like 20 might (for some purposes) be a good value.

```{r guess twenty}
display(img[, , 1, 1] > 20)
```

But what if we have many images and we don't want to *play around*, we want a method of calculating the threshold automatically. http://imagej.net/Auto_Threshold gives many such methods and they are provided to you in R via this package. Go to that webpage for a nice comparison of the methods.

The function `auto_thresh()` finds the threshold, `auto_thresh_mask()` gets the mask (an array with a `TRUE` for elements exceeding the threshold and `FALSE` elsewhere) and `auto_thresh_apply_mask()` applies the mask to the original image by setting the elements that don't exceed the threshold to `NA`.

Let's see each with Huang thresholding.

```{r thresh mask apply}
auto_thresh(img, "huang")
auto_thresh_mask(img, "huang") %>% {display(.[, , 1, 1])}
auto_thresh_apply_mask(img, "huang") %>% {display(.[, , 1, 1])}
```

In this last image, the `NA` pixels are white

## Stacks of Images
We can do the same thing with an image stack.
```{r the image stack}
img <- read_tif(system.file("extdata", "50.tif", 
                            package = "autothresholdr"))
dim(img)
display(img[, , 1, 1])
mean_stack_thresh(img, "tri") %>% {display(.[, , 1, 1])}
med_stack_thresh(img, "tri") %>% {display(.[, , 1, 1])}
```

These are indeed (on close inspection) slightly different.
